Support

### 2022-05-25 analyses/supportStudy.Rmd
cleaned, licensed version of cbnn

---
title: "iterSim"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 2
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.5
---

@@

```{python}

import os
os.environ["CUDA_DEVICE_ORDER"] = "PCI_BUS_ID" 
os.environ["CUDA_VISIBLE_DEVICES"] = ""

@@

hardsim<-T
numSamp<-2000
```

```{r complexPrep,eval=hardsim}

##############################
###set up complex simulation
##############################

# Define a function returning the log cum hazard at time t
logcumhaz <- function(t, x, betas, knots) {

  # Obtain the basis terms for the spline-based log
  # cumulative hazard (evaluated at time t)
  basis <- flexsurv::basis(knots, log(t))

  # Evaluate the log cumulative hazard under the
  # Royston and Parmar specification
  res <-betas[["gamma0"]] * basis[[1]] + 
    betas[["gamma1"]] * basis[[2]] +
    betas[["gamma2"]] * basis[[3]] +
    betas[["gamma3"]] * basis[[4]] +
    betas[["gamma4"]] * basis[[5]] +
    betas[["z1"]] * x[["z1"]]+
    betas[["z2"]] * x[["z2"]]+
    betas[["z3"]] * x[["z3"]]+
    betas[["term1"]] * x[["z1"]]*x[["z2"]]*t+
    betas[["term2"]] * x[["z1"]]*x[["z3"]]+
    betas[["term3"]] * x[["z2"]]*(x[["z3"]])
  #
  # Return the log cumulative hazard at time t
  res
}
url<-'app.txt'
ds <- read.table(url, sep = '',header = TRUE)
ds$years.at.risk=pmin(ds$agein80,ds$onset)
brcancer$rectime<-brcancer$rectime/max(brcancer$rectime)
true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1, data = brcancer, k = 3) #from flexsurv

# Simulate the event times
coefficients<-true_mod$coefficients
coefficients<-c(coefficients,z1=1,z2=1,z3=1,term1=10,term2=2,term3=2)

@@

```{r totalSim,eval=hardsim}

start_time <- Sys.time()
BrierIPAList<-list()
cScore<-list()
pos<-1

@@

  #########################
  ###Simulate date
  #########################
  cov<-data.frame(id=1:numSamp,
                  z1=c(rep(1,numSamp/2),rep(0,numSamp/2)),
                  z2=c(rnorm(numSamp/2,10,0.5),rnorm(numSamp/2,0,0.5)),
                  z3=c(rnorm(numSamp/2,-3,0.5),rnorm(numSamp/2,8,0.5)))
  true_mod <- flexsurv::flexsurvspline(Surv(rectime, censrec) ~ 1,
                                       data = brcancer, k = 3
  ) #from flexsurv
  dat <- simsurv(betas = coefficients, # "true" parameter values
                 x = cov,                   # covariate data for 200 individuals
                 knots = true_mod$knots,    # knot locations for splines
                 logcumhazard = logcumhaz,  # definition of log cum hazard
                 maxt = 1,               # no right-censoring
                 interval = c(0,10000000)) # interval for root finding
  colnames(dat)<-c("id","time","status")
  samp<-sample(seq(1,nrow(dat),by=1), floor(nrow(dat)*(0.1))) #random censoring
  dat$status[samp]<-0
  # Merge the simulated event times onto covariate data frame
  data <- merge(cov, dat)
  covs<-colnames(data)

  #########################
  ###Simulate data
  #########################
  samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.8))
  data<-data[,-1]
  data[,-c(1,5)]<-as.data.frame(sapply(data[,-c(1,5)], function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))
  train<-data[samp,]
  test<-data[-samp,-c(ncol(data))]
  fullTest<-data[-samp,,drop=F]
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

  ###########################
  ###casebase optimal model
  ###########################
  final_mod_cb_glm <- fitSmoothHazard(status~bs(time)-time+z1+z2+z3+z1:z2:time+z1:z3+z2:z3,
                                      data = train,
                                      time = "time",
                                      event="status",
                                      ratio = 100
  )

  summary(final_mod_cb_glm)
  tglmAbsRisk<-absoluteRisk(final_mod_cb_glm,time=times,newdata=test,type="CI")
  tglmAbsRisk<-as.data.frame(tglmAbsRisk)
  rownames(tglmAbsRisk)<-tglmAbsRisk$time
  trueGlmProper<- t(tglmAbsRisk[-1,-1])
  class(trueGlmProper)<-c("tunnel",class(trueGlmProper))

  #########################
  ###casebase+splines
  #########################
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

  glmAbsRisk<-absoluteRisk(mod_cb_glm,time=times,newdata=test,type="CI")

  glmAbsRisk<-as.data.frame(glmAbsRisk)

  rownames(glmAbsRisk)<-glmAbsRisk$time
  glmProper<- t(glmAbsRisk[-1,-1])

  class(glmProper)<-c("tunnel",class(glmProper))

@@

  ######################
  ###coxph
  ######################
  cox<-coxph(Surv(time, status) ~ z1+z2+z3, data = train,x=T)

@@

  brierFinalResults <- Score(list("Cox_Lin" = cox,
                                  'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,
                                  'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,
                                  'Optimal'=trueGlmProper,
                                  'PMNN_Poly'=annProperpoly),
                             #'dsm'=dsmSurvProper) ,#'dsm'=dsmCleaned,
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

@@

  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 trueGlmProper,
                 annProperpoly
  )

  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(train)[,c(5,4)]
  et_test<-as.matrix(fullTest[,c(5,4)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','Optimal','PMNN_Poly')#,'dsm')
  cScoreTemp[,1]<- tempTims

@@

  saveRDS(BrierIPAList,'results/100hardBrier.rds')
  saveRDS(cScore,'results/100hardcidx.rds')
  pos<-pos+1
}

@@

>>>>

---
title: "Support"
output: html_document
params:
  epo: 2000
  patience: 10
  iteration: 2
  layer1: 50
  layer2: 50
  layer3: 25
  layer4: 25
  drpt: 0.5
---

```{r,eval=T}

@@

```{python,eval=T}

import os
os.environ["CUDA_DEVICE_ORDER"] = "PCI_BUS_ID" 
os.environ["CUDA_VISIBLE_DEVICES"] = ""
#os.environ["OM_NUM_THREADS"]="2"

@@

@@

```{r modelsSUPPORT,eval=eval_support}

start_time <- Sys.time()
BrierIPAList<-list()
cScore<-list()

data<- as.data.frame(do.call(cbind, getSupportPycox()))
colnames(data)[ncol(data)-1]<-'time'
colnames(data)[ncol(data)]<-'status'
data<-as.data.frame(model.matrix(~.,data)[,-1])
data<-as.data.frame(sapply(data, function(x) (x - min(x, na.rm = T)) / (max(x, na.rm = T) - min(x, na.rm=T))))

covs<-colnames(data)

#split training/testing
samp<-sample(seq(1,nrow(data),by=1), floor(nrow(data)*.80)) 
trainOG<-data[samp,]
test<-data[-samp,-c(ncol(data))]
fullTest<-data[-samp,,drop=F]

pos<-1

@@

  samp<-sample(seq(1,nrow(trainOG),by=1) , nrow(trainOG),replace = T) 
  train<-trainOG[samp,]
  times<-seq(from=min(test$time),
             to=max(test$time),
             length.out = 200
  )
  times<-times[-c(1,length(times))]

  ######################
  ###casebase + splines
  ######################
  mod_cb_glm <- fitSmoothHazard(status~bs(time)+.-time,
                                data = train,
                                time = "time",
                                event="status",
                                ratio = 100
  )

  glmAbsRisk<-as.data.frame(absoluteRisk(mod_cb_glm,time=times,newdata=test,type="CI"))
  rownames(glmAbsRisk)<-glmAbsRisk$time
  #prepare to run through riskRegression
  glmProper<- t(glmAbsRisk[-1,-1])
  class(glmProper)<-c("tunnel",class(glmProper))

@@

  ######################
  ###coxph
  ######################
  cox<-coxph(Surv(time, status) ~ ., data = train,x=T)

@@

  ######################
  ###IPA metric
  ######################
  brierFinalResults <- Score(list("Cox_Lin" = cox,'CB_Logi'=glmProper,
                                  'DeepSurv'=cnnCleaned,'DeepHit'=deephitCleaned,
                                  'PMNN_Spline'=annProper,'PMNN_Poly'=annProperpoly),
                             data =fullTest, 
                             formula = Hist(time, status != 0) ~ 1, summary = c("risks","IPA","ibs"), 
                             se.fit = FALSE, metrics = "brier", contrasts = FALSE, times = times)
  BrierIPAList[[pos]]<-brierFinalResults$Brier$score

@@

  riskList<-list(coxlinSurv,
                 glmProper,
                 cnnCleaned,
                 deephitCleaned,
                 annProper,
                 annProperpoly
  )

  tempTims<-   as.numeric(colnames(annProper))
  tempTims<-head(tempTims, -1)
  tempTims<-tail(tempTims, -1)
  cScoreTemp<-matrix(NA,nrow=length(tempTims),ncol=length(riskList)+1)
  et_train<-as.matrix(train)[,c(16,15)]
  et_test<-as.matrix(fullTest[,c(16,15)])
  colnames(cScoreTemp)<-c('times', "Cox_Lin",'CB_Logi','DeepSurv','DeepHit',
                          'PMNN_Spline','PMNN_Poly')
  cScoreTemp[,1]<- tempTims

@@

  saveRDS(BrierIPAList,'results/100supBrier.rds')
  saveRDS(cScore,'results/100supcidx.rds')
  pos<-pos+1
}

ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=Brier,col=model))+
  geom_line()
ggplot(data=brierFinalResults$Brier$score, aes(x=times,y=IPA,col=model))+
  geom_line()

end_time <- Sys.time()

end_time-start_time

@@

sessionInfo()
